### 2021-07-09 rad-icfp-2021/correctness.tex
.

\begin{definition}[Mutlicategory from concat]
    We define $\CSource$ to be the multicategory with the same objects as Source and\\ 
    $\CSource([A_1,\ldots,A_n],B)=\{f\in\ConcatS([A_1,\ldots,A_n],[A_1,\ldots,A_n,B], \forall i.f;\pi_{A_i}=id_{A_i})$.
    The composition of $f_i:\underline{A}_i\to B_i$ with $g:\underline{B}\to C$ is given 
    $f_1\concatcomp\ldots\concatcomp f_n;(u_{\underline{B}_1}\concatcomp A_1 \concatcomp \ldots \concatcomp u_{\underline{B}_n}\concatcomp A_n);g$.
    In other words each term $f_i$ forgets about its output $\underline{B}_i$, and then we use the composition in the concategory.
\end{definition}

>>>>

\begin{definition}[Mutlicategory from concat]
    We define $\CSource$ to be the multicategory with the same objects as Source and\\ 
    $\CSource([A_1,\ldots,A_n],B)=\{f\in\ConcatS([A_1,\ldots,A_n],[A_1,\ldots,A_n,B], \forall i.f;\pi_{A_i}=id_{A_i})$\\
    The composition of $f_i:\underline{A}_i\to B_i$ with $g:\underline{B}\to C$ is given 
    $f_1\concatcomp\ldots\concatcomp f_n;(u_{\underline{B}_1}\concatcomp A_1 \concatcomp \ldots \concatcomp u_{\underline{B}_n}\concatcomp A_n);g$.
    In other words each term $f_i$ forgets about its output $\underline{B}_i$, and then we use the composition in the concategory.
\end{definition}
